\section{Experiment}

\subsection{Measuring converging lenses}
\subsubsection{Lens equation}
To calculate the focal length $f$ using the lens equation, we need to place an object, in our case a wired net, in front of a monochromatic LED light. 
The light then passes through the lens we want to measure and the image is projected on to a white screen.
Now the goal is to adjust the position of the lens, so that the image is as sharp as possible.
That gives us two distances:
first $a$ between object and lens, and then $b$ between lens and image.
We are then able to calculate the focal length using
\begin{equation}
	\displaystyle f = \frac{ab}{a+b}
	\label{eq::lens}
\end{equation}





\subsubsection{Bessel's Method}
Now we want to use Bessel's method.
Here we have to measure slightly different things.
With the same setup, we take a fixed distance $d$ between the object and the image. 
By varying the location of the lense in between, we are able to find two spots, where there is a sharp image, once magnified, once demagnified.
We measure the distance $e$ between those two positions. Then we calculate $f$ using
\begin{equation}
	f = \frac{d^2 - e^2}{4d}
	\label{eq::bessel}
\end{equation}


\subsection{Measuring diverging lenses}
To measure the focal length of a diverging lens $f_{div}$, we have to set a converging one with focal length $f_{conv}$ behind it (or in front). 
Then we measured the focal length $f$ of the resulting lens system like before using the lens equation (\ref{eq::lens}).
We can now use the following equation to determine $f_{div}$:
\begin{equation}
	\frac{1}{f} = \frac{1}{f_{div}} + \frac{1}{f_{conv}} \implies f_{div} = \frac{f_{conv} f}{f_{conv} - f}
	\label{eq::div}
\end{equation}


\subsection{Measuring wired nets}
Here we want to measure the grating constant $g$ of a wired net.
To do that, we image the wired net to the screen using a lens with a known focal length.
As in the beginning, we try to get the sharpest image possible by adjusting the position of the lens and get $a$ and $b$ like before.
From that, we get the magnification scale $v = b/a$
We can then measure the grid width $g'$ of the image, and calculate $g$ by using this equation:
\begin{equation}
	g = \frac{g'}{v}
	\label{eq::grid}
\end{equation}

\subsection{Critical slit width}

